On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-19 Manuscript/manuscript.tex
Condensed a Little Bit

Block bootstrap is a powerful tool for constructing confidence intervals (CI)
when making inferences about dependent data. Early ideas were developed
independently by 
\citet{hall1985resampling, carlstein1986use,ckunsch1989jackknife}.
It has since been applied in various fields such as econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is particularly useful for serially dependent
data when the serial dependence is not specified or not of primary interest.
The method is expected to produce CIs with coverage rates
matching their nominal levels as the sample size grows to infinity. However,
when dealing with finite sample sizes, an important question is how large the
sample size needs to be for block bootstrap CIs to have the
desired coverage rates.

\jy{too wordy; do some condensing}
The performance of bootstrap standard errors with independent data
in providing valid uncertainty measures has been extensively studied.
For example, for non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs for the mean from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
that the best choice of method for estimating
the parameter of a distribution is dependent on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural
equation modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. In estimating the proportion of 
variation attributable to certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (standard, percentile, and 
bias-corrected
and accelerated) approach the coverage of a pivotal quantity as the sample size
gets larger for an underlying normal distribution, but for other distributions, 
coverage may deteriorate even as the sample size increases.
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample of size of 100 and the correlation coefficient is equivalent to 0.
The general consensus is that a big sample size is necessary.

@@

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data, similar to what 
was done for basic bootstrap in \citet{hesterberg2015teachers}. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare six variants of block bootstrap
CIs from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a standard normal CI, and a Student's $t$ CI,
a percentile CI, a bias-corrected CI, a bias-correct and accelerated ($BC_a$)
CI, and a CI proposed in this article. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent
on the type of interval used.

>>>>

Block bootstrap is a tool to construct confidence intervals (CI)
to make inferences about dependent data. Early ideas were developed
independently by 
\citet{hall1985resampling, carlstein1986use,ckunsch1989jackknife}.
It has since been applied in various fields such as econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is useful for serially dependent
data when the serial dependence is not specified or not of primary interest.
The method is expected to produce CIs with coverage rates
matching their nominal levels as the sample size grows. However,
when dealing with finite sample sizes, an important question is how large the
sample size must be for block bootstrap CIs to have the
desired coverage rates.

\jy{too wordy; do some condensing} \mc{condensed a little bit}
The performance of bootstrap standard errors with independent data
in providing valid uncertainty measures has been extensively studied.
For example, for non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs for the mean from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
that the best method to estimate
the parameter of a distribution depends on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural
equation modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is sufficient for interval estimation
using standard nonparametric bootstrap. In estimating the proportion of 
variation attributable to a certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (standard, percentile, and 
bias-corrected
and accelerated) approach the coverage of a pivotal quantity as the sample size
gets larger for an underlying normal distribution, but for other distributions, 
coverage may deteriorate as the sample size increases.
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample with size~$100$ and correlation coefficient equal to 0.
The general consensus is that a big sample size is necessary.

@@

The goal of this paper is to provide recommendations on
necessary sample size for block bootstrap with dependent data, similar to what 
was done for basic bootstrap in \citet{hesterberg2015teachers}. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare six variants of block bootstrap
CIs from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a standard normal CI, and a Student's $t$ CI,
a percentile CI, a bias-corrected CI, a bias-correct and accelerated ($BC_a$)
CI, and a CI proposed in this article. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that recovery of temporal dependence parameters is reliant
on the type of interval used.
